---
title: "Data Science 871 project"
output: github_document
---

## Media Consumption and Willingness to upgrade internet package.

The purpose of this project is to use survey data in order to determine which factors are important predictors of whether individuals would be willing to upgrade their internet packages. 

```{r include=FALSE }

rm(list = ls()) 
gc()

library(tidyverse)
```

Code files:
```{r echo=FALSE}
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

## Data loading and cleaning
The data set contains survey responses from 2131 individuals regarding demographic factors (age, sex, race, ect.), the types of apps they use, time spent on different devices, preferred type of media, and other issues regarding media consumption. 

The first step is converting factor variables to features and converting answers to a question that was reported in multiple columns to one column

```{r}
masterDF <- read.csv('data/DeloitteMediaConsumptionSurvey.csv')
head(demographicDF)
    

```
